Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
delete a paragraph inline paper for ux sprint
Add a walkthrough graphic.
I went in to VLC, turned on subtitles, "Take Snapshot", opened in Gimp,
resized to 3.4 inches wide at 150 dpi.

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{walkthrough.png}
\caption{
A participant narrates their thinking
while downloading Tor Browser.
% https://people.torproject.org/~dcf/uxsprint2015/p3.srt
{
\it
``There's this big purple icon on the left side of the screen that says `Download Tor Browser',
so I'm going to click on that because it seems like the most obvious thing.
There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.''
}
}
\label{walkthrough}
\end{figure}
